Universal Anonymous Signatures

### 2022-08-17 prism-backend/research/gsac/formal-uas.tex
Refining

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  honest {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  corrupt {\uid}s/{\iid}s/{\oid}s.
\item[\UK,\IK,\OK.] Tables maintaining key pairs of users $(\upk,\usk)$, issuers
  $(\ipk,\isk)$, and openers $(\opk,\osk)$. They are indexable by \uid,
  \iid, and \oid, respectively. Also, issuers' public keys contain their \fissue
  function, and openers' public keys contain their \finsp function.
\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
  keys ($\mathsf{SXK}$).
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but tracks challenge credentials in the issuance
  anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no wuch \uid. We may also use \OWNR over a set of {\cid}s
  (\scid). In that case, our convention is that $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

\begin{theorem}[Unforgeability of \CUASGen]
  \label{thm:forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
  extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
  unforgeable, then our \CUASGen construction
  satisfies unforgeability as defined in \defref{def:sign-forge-uas}, except
  with negligible probability.
\end{theorem}

>>>>

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  honest {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
  corrupt {\uid}s/{\iid}s/{\oid}s.
\item[\UK,\IK,\OK.] Tables maintaining key pairs of users $(\upk,\usk)$, issuers
  $(\ipk,\isk)$, and openers $(\opk,\osk)$. They are indexable by \uid,
  \iid, and \oid, respectively. Also, issuers' public keys contain their \fissue
  function, and openers' public keys contain their \finsp function.
\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
  keys ($\mathsf{SXK}$).
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but tracks challenge credentials.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
  $\bot$ if there is no wuch \uid. We may also use \OWNR over a set of {\cid}s
  (\scid). In that case, our convention is that $\OWNR[\scid]$ returns $\bot$ if
  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
  \uid, all conditions checking membership of the output of \OWNR to a list of
  users equal false if \OWNR returns $\bot$.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

\begin{theorem}[Unforgeability of \CUASGen]
  \label{thm:forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
  extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
  unforgeable, then our \CUASGen construction
  satisfies unforgeability as defined in \defref{def:forge-uas}, except
  with negligible probability.
\end{theorem}

### 2022-08-17 prism-backend/research/gsac/introduction-paper.tex
Refining

This separation does not hold in the approaches to build them, though. The
probably most fruitful way to design and instantiate AC systems
is with CL-type signatures \cite{cl02}. But the fact that they support efficient
zero-knowledge protocols for proving knowledge of a signature, makes them very
suitable to build GS schemes -- even without exploiting the possibility to
encode many attributes. Indeed, BBS+ signatures \cite{bbs04,cdl16b} have been
used to design and instantiate GS schemes \cite{gl19,dl21}, as well as  PS16
signatures \cite{ps16,cdl+20}. Both are CL-like signature schemes, and thus
can be (and have been) used to design AC schemes \needcite.

@@

\paragraph{Generic construction, and connections with previous schemes.} %
We give a main generic construction based on well-known building blocks, and
prove its security. To prove its universality, we show how restrictions of our
generic construction directly imply the direct ancestors of UAS: group
signatures and anonymous credentials. This includes not only their vanilla
versions, but also relevant variants, such as MPS \cite{ngsy22}, (a modified
version of) group signatures with message-dependent opening \cite{seh+12}, or
anonymous credentials with revocation \cite{cks10} or delegation \cite{bcc+09}.
Strictly speaking, for AC schemes, we build on a simple transform of our main
construction and model that turns non-interactive signatures into interactive
authentication protocols with protection against replay attacks\footnote{This is
  the well-known folklore approach that has the verifier send a fresh nonce to
  be signed.}. We further show how to build ring signatures (RS) in the model
given by \cite{bkm06}, from an alternative construction that improves issuer
privacy.
%
The most interesting part being that, while we prove implications with other
previously known schemes, our generalisation approach allows to merge features
of them: e.g., one can easily model and instantiate GSs with with no revocation
at all, ACs with full de-anonymization, RS with linkability, or anything in
between -- like being able to deanonymize only if certain conditions are met.

>>>>

This separation does not hold in the approaches to build them, though. The
probably most fruitful way to design and instantiate AC systems
is with CL-type signatures \cite{cl02}. But the fact that they support efficient
zero-knowledge protocols for proving knowledge of a signature, makes them very
suitable to build GS schemes -- even without exploiting the possibility to
encode many attributes. Indeed, BBS+ signatures \cite{bbs04,cdl16b} have been
used to design and instantiate GS schemes \cite{gl19,dl21}, as is the case for
PS16 signatures \cite{ps16,cdl+20}.

@@

\paragraph{Generic construction, and connections with previous schemes.} %
We give a main generic construction based on well-known building blocks, and
prove its security. To prove its universality, we show how restrictions of our
generic construction directly imply the direct ancestors of UAS: group
signatures and anonymous credentials. This includes not only their vanilla
versions, but also relevant variants, such as MPS \cite{ngsy22}, (a modified
version of) group signatures with message-dependent opening \cite{seh+12}, or
anonymous credentials with revocation \cite{cks10} or delegation \cite{bcc+09}.
Strictly speaking, for AC schemes, we build on a simple transform of our main
construction and model that turns non-interactive signatures into interactive
authentication protocols with protection against replay attacks\footnote{This is
  the well-known folklore approach that has the verifier send a fresh nonce to
  be signed by the alleged owner of the private key related to a known
  public key.}. We further show how to
build ring signatures (RS) in the model given by \cite{bkm06}, from an
alternative construction that improves issuer privacy.
%
The most interesting part being that, while we prove implications with other
previously known schemes, our generalisation approach allows to merge features
of them: e.g., one can easily model and instantiate GSs with with no revocation
at all, ACs with full de-anonymization, RS with linkability, or anything in
between -- like being able to deanonymize only if certain conditions are met.

### 2022-08-17 prism-backend/research/gsac/uas-paper.tex
Refining

\begin{document}
{\def\addcontentsline#1#2#3{}\maketitle}%\maketitle

\begin{abstract}
  \todo{XXX}
\end{abstract}

>>>>

\begin{document}
{\def\addcontentsline#1#2#3{}\maketitle}%\maketitle
\ifnum\authnotes=1
Version of \today
\fi

\begin{abstract}
  For decades, anonymous credentials, group signatures, and closely related
  systems in the domain of privacy-preserving authentication, have relied on
  common cryptographic building blocks. However, each has its own approach
  modelling-wise, despite obvious commonalities.
  %
  Even within systems of the same type, multiple ``sub-models'' and
  constructions coexist that cater for slightly different requirements.

  Previous works, like Camenisch et al in SAC'15, or Nguyen et al in CRYPTO'22
  generalize aspects of those systems, but still within their own domain --
  anonymous credentials and group signatures, respectively.

  In this work, we make a significant generalization effort in order to come
  up with a flexible game-based model that subsumes
  previous ones. The key to this flexibility lies in functional placeholders
  that, with careful constraints, still allow to capture generalized notions of
  the usual anonymity, unforgeability and non-frameability properties. We refer
  to this unified model as \emph{Universal Anonymous Signatures} (\UAS).

  To showcase the generality of \UAS, we give a main construction, plus two
  alternative ones that slightly modify it, following our \UAS model.
  We prove that, from these constructions, we can build multiple variants of
  group signatures, anonymous credentials, and ring signatures, just by giving
  concrete definitions of the mentioned functional placeholders.

  Our main theoretical contribution is unifying previously separate
  (albeit close) systems under the same generalized model. Indeed, such unified
  model allows to, very easily, build ``hybrid'' systems that combine features
  of previously separately modelled constructions: e.g., anonymous credentials
  with conditional deanonymization based on their attributes.

  More practically, this has the consequence that cryptographic
  engineers and system designers can tweak the desired utility-vs-privacy
  tradeoff that best suits their needs, just by defining a few functions --
  but without needing to prove security from scratch or implement
  a whole system.
\end{abstract}
